---
title: "ECON294.lab.Final.YeLi.1505112"
output: html_document
---

#Set up
```{r set up,warning=FALSE,echo=F,message=FALSE}
library(ggplot2)
library("dplyr")  
library("RSQLite") 
library("nycflights13") 

my_db <- nycflights13_sqlite()


flights_weather1<-left_join(
  tbl(my_db, "flights"),
  tbl(my_db, "weather"),
  by = c("year","month","day","hour"))%>% 
  collect() %>%
  mutate(canceled = is.na(arr_time))

flights_weather1$month<-as.factor(flights_weather1$month)
flights_weather2<-subset(flights_weather1,arr_delay>=60|dep_delay>=60)

```

#---(a)Weather---#
###Regression
```{r regression,warning=FALSE,echo=T,eval=F,message=FALSE}
reg_delayed<-lm(dep_delay~temp+dewp+humid+wind_dir+wind_speed++wind_gust+precip+pressure+visib,flights_weather1)
summary(reg_delayed)

reg_canceled<-lm(canceled~temp+dewp+humid+wind_dir+wind_speed++wind_gust+precip+pressure+visib,flights_weather1)
summary(reg_canceled)
```
From the regression results,dewpoints, preciptation and wind speed has significantly increased delay, while only dewpoints has significanlty increased the probability of being canceled.

###Graph
Below is the relationship between preciptation and delayed.
```{r graph,warning=FALSE,echo=T,message=FALSE}
a<-ggplot(data = sample_n(flights_weather2, 10000),aes(x=precip,y=dep_delay))
a+geom_point()+geom_line()
```

#---(b)Time---#

###Group_by
```{r group_by,warning=FALSE,echo=T,message=FALSE}

delaysum<- tbl(my_db, "flights") %>%
  group_by(year, month, day) %>%
  summarize(
    delaymean = mean(dep_delay)
  ) %>% collect()

```
###1.Time of Day
```{r, warning=F,echo=F,message=FALSE}

c<-ggplot(delaysum,aes(x=day,y=delaymean)) 
c+geom_point()+geom_line()
```
From graph, it looks like around 9am, there's a significant higher delay than others.

###2.Day of Month
```{r, warning=F,echo=F,message=FALSE}

d<-ggplot(delaysum,aes(x=month,y=delaymean)) 
d+geom_point()+geom_line()
```
From graph, it looks light March has a significant higher chance of delay.

###3.Time of year(Regression)
```{r regression2,warning=FALSE,echo=T,eval=F,message=FALSE}
reg1<-lm(dep_delay~month,flights_weather2)
summary(reg1)
reg2<-lm(canceled~month,flights_weather2)
summary(reg2)
```
Month 1, 6 and 9 has significant delay. This might due to high volume of passengers
Month 7 has significant cancel. This might due to high probability of preciptation.


#---(c)Airport Destination---#

```{r,warning=FALSE,message=FALSE}

dest_delay<-flights_weather2 %>%
  filter(!is.na(arr_delay)) %>%
  group_by(dest) %>%
  summarize(
    delay=mean(arr_delay),
    n=n()
  ) %>%
  arrange(-delay) %>%
  print(head(5))
```
The destination that has highest average delay is CAE, TUL and OKC.


#---(d)characteristics of the plane-----#
```{r,echo=F,warning = F,include=F}
my_db <- nycflights13_sqlite()
flights_planes1<-left_join(
  tbl(my_db, "flights"),
  tbl(my_db, "planes"),
  by = "tailnum")%>% 
  collect() %>%
  mutate(canceled = is.na(arr_time))
```

###Regression
```{r,echo=F,warning = F,include=T}
r1<-lm(dep_delay~engines+seats+engine,flights_planes1)
summary(r1)
r2<-lm(canceled~engines+seats+engine,flights_planes1)
summary(r2)
```
The results show that engines will significantly increase the probability of being canceled. 







